---
title: "Diamond sizes"
date: 2016-08-25
output: html_document
---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
smaller <- diamonds %>% 
  filter(carat <= 2.5)
sizes <- c("small", "medium", "large")
dg <- diamonds %>% 
  mutate(size_group = cut_number(carat, 3, labels=sizes)) 

knitr::opts_chunk$set(
  echo = FALSE
)
```

We have data about `r nrow(diamonds)` diamonds. Only 
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

The peaks represent whole number sizes


## Diamond size vs cut
```{r Size_Cut}
dg %>% 
  ggplot() +
    geom_bar(aes(x = size_group, fill = cut),
             position = "fill")

```
Here, you can see that proportioin of Ideal goes down with size, but there is not a linear relationship with the other values, for example proportion of fair goes up in medium but down in large, same with good.

## Diamond size vs color
```{r Size_color}
dg %>% 
  ggplot() +
    geom_bar(aes(x = size_group, fill = color),
             position = "fill")

```
Here, you can see proportion of D and E go down with size while the proportions of H, I and J go up a lot with size

## Diamond size vs clarity
```{r Size_clarity}
dg %>% 
  ggplot() +
    geom_bar(aes(x = size_group, fill = clarity),
             position = "fill")

```
The proportion of SI1 and SI2 go down with increasing size while the proportions of IF, WS1 and WS2 all go up with increasing size.

