--
title: "Diamond sizes"
date: 2016-08-25
output: html_document
---

```{r setup, include = FALSE}
library(ggplot2)
library(tidyverse)
smaller <- diamonds %>% 
  filter(carat <= 2.5)

comma <- function(x) format(x, digits = 2, big.mark = ",")
```

We have data about `r comma(nrow(diamonds))` diamonds. Only 
`r comma(nrow(diamonds) - nrow(smaller))` are larger than
2.5 carats (that is, `r comma((nrow(diamonds) - nrow(smaller))*100/nrow(diamonds))` %). The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

##  The largest 20 Diamonds

```{r get_largest_20}

largest_20 <- diamonds %>% 
  mutate(rank=row_number(desc(carat))) %>% 
  mutate(size_group = if_else(rank <= 20, "Top 20", "Others")) %>% 
  arrange(rank)
```


```{r Size_Cut}
largest_20 %>% 
  ggplot() +
    geom_bar(aes(x = size_group, fill = cut),
             position = "fill")

```
A massive increase in fair diamonds and a massive decrease in ideal diamonds

## Diamond size vs color
```{r Size_color}
largest_20 %>% 
  ggplot() +
    geom_bar(aes(x = size_group, fill = color),
             position = "fill")

```
Colour J,I, H dominate the top 20

## Diamond size vs clarity
```{r Size_clarity}
largest_20 %>% 
  ggplot() +
    geom_bar(aes(x = size_group, fill = clarity),
             position = "fill")

```
The Top 20 are almost completely I1, SL2 and SL2


```{r}
knitr::kable(
  largest_20 %>% 
    filter(rank <= 20) %>% 
    select(carat:clarity, price, rank),
  caption = "Characteristics from the largest 20 diamonds"
)

```

